---
title: "Data Processing"
author: "Jieyuan Yan, Puwen Wen"
format: html
---

## Prepare environment
```{r}
library(here)
library(vroom)
library(tidyr)
library(dplyr)
```

## Read Dataset
```{r}
urb_cpopcb = vroom('dataset//estat_urb_cpopcb.tsv',delim = "\t",show_col_types = FALSE)
ilc_di16 = vroom('dataset//estat_ilc_di16.tsv',delim = "\t",show_col_types = FALSE)
ilc_iw16 = vroom('dataset//estat_ilc_iw16.tsv',show_col_types = FALSE)
ilc_peps06 = vroom('dataset//estat_ilc_peps06.tsv',show_col_types = FALSE)
ilc_lvps16 = vroom('dataset//estat_ilc_lvps16.tsv',show_col_types = FALSE)
edat_lfs_9912 = vroom('dataset//estat_edat_lfs_9912.tsv',show_col_types = FALSE)
lfsa_pfgacedm = vroom('dataset//estat_lfsa_pfgacedm.tsv',show_col_types = FALSE)
lfst_r_lfur2gacu = vroom('dataset//estat_lfst_r_lfur2gacu.tsv',show_col_types = FALSE)
lfst_r_eredcobu = vroom('dataset//estat_lfst_r_eredcobu.tsv',show_col_types = FALSE)
```

## Deal with Dataset

urb_cpopcb: Population by citizenship and country of birth - cities and greater cities
```{r}

urb_cpopcb = urb_cpopcb |> separate(`freq,indic_ur,cities\\TIME_PERIOD`, 
                            into = c("freq", "indic_ur", "cities"), 
                       sep = ",")
urb_cpopcb = urb_cpopcb|>
  pivot_longer(cols = `1990`:`2024`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )

```

ilc_di16: Mean and median income by group of country of birth (population aged 18 and over)
```{r}

ilc_di16 = ilc_di16 |> separate(`freq,unit,indic_il,c_birth,sex,age,geo\\TIME_PERIOD`, 
        into = c("freq", "unit", "indic_il","c_birth","sex","age","geo"), 
        sep = ",")
ilc_di16 = ilc_di16|>
  pivot_longer(cols = `2003`:`2023`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )
```


ilc_iw16: In-work at-risk-of-poverty rate by group of country of birth(population aged 18 and over)
```{r}

ilc_iw16 = ilc_iw16 |> separate(`freq,unit,c_birth,sex,age,geo\\TIME_PERIOD`, 
        into = c("freq", "unit","c_birth","sex","age","geo"), 
        sep = ",")
ilc_iw16 = ilc_iw16|>
  pivot_longer(cols = `2003`:`2023`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )
```


ilc_peps06: Persons at risk of poverty or social exclusion by group of country of birth (population aged 18 and over)
```{r}
# Persons at risk of poverty or social exclusion
# unit: percentage

ilc_peps06 = ilc_peps06 |> separate(`freq,c_birth,sex,age,unit,geo\\TIME_PERIOD`, 
        into = c("freq", "unit","c_birth","sex","age","geo"), 
        sep = ",")
ilc_peps06 = ilc_peps06|>
  pivot_longer(cols = `2003`:`2020`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )
```


ilc_lvps16: Distribution of population by group of country of birth and tenure status (population aged 18 and over)
```{r}
# Distribution of population by group of country of birth and tenure status
ilc_lvps16 = ilc_lvps16 |> separate(`freq,unit,tenure,c_birth,sex,age,geo\\TIME_PERIOD`, 
        into = c("freq","unit","tenure","c_birth","sex","age","geo"), 
        sep = ",")
ilc_lvps16 = ilc_lvps16|>
  pivot_longer(cols = `2003`:`2023`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )

```


edat_lfs_9912: Population by educational attainment level, sex, age and country of birth
```{r}

edat_lfs_9912 = edat_lfs_9912 |> separate(`freq,unit,sex,isced11,c_birth,age,geo\\TIME_PERIOD`, 
        into = c("freq","unit","sex","isced11","c_birth","age","geo"), 
        sep = ",")
edat_lfs_9912 = edat_lfs_9912|>
  pivot_longer(cols = `2004`:`2023`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )
```


lfst_r_lfur2gacu: Unemployment rates by sex, age, country of birth and degree of urbanisation
```{r}

lfst_r_lfur2gacu = lfst_r_lfur2gacu |> separate(`freq,unit,deg_urb,c_birth,sex,age,geo\\TIME_PERIOD`, 
        into = c("freq","unit","deg_urb","c_birth","sex","age","geo"), 
        sep = ",")
lfst_r_lfur2gacu = lfst_r_lfur2gacu|>
  pivot_longer(cols = `1995`:`2023`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )
```


lfst_r_eredcobu: Employment rates by sex, age, educational attainment level, country of birth and degree of urbanisation
```{r}

lfst_r_eredcobu = lfst_r_eredcobu |> separate(`freq,deg_urb,c_birth,isced11,age,sex,unit,geo\\TIME_PERIOD`, 
        into = c("freq","deg_urb","c_birth","isced11","age","sex","unit","geo"), 
        sep = ",")
lfst_r_eredcobu = lfst_r_eredcobu|>
  pivot_longer(cols = `1995`:`2023`,
    names_to = "TIME_PERIOD",
    names_transform = as.integer,
    values_to = "values"
  )
```




