---
title: "Data Processing"
author: "Jieyuan Yan, Puwen Wen"
format: html
---

## Prepare environment
```{r}
library(here)
library(vroom)
library(tidyr)
library(dplyr)
library(eurostat)
```

## Read Dataset
```{r}
urb_cpopcb <- get_eurostat('urb_cpopcb',time_format = "num", stringsAsFactors = TRUE)
ilc_di16 <-  get_eurostat('ilc_di16',time_format = "num",stringAsFactors = TRUE)
ilc_iw16 <-  get_eurostat('ilc_iw16',time_format = "num",stringAsFactors = TRUE)
ilc_peps06 <-  get_eurostat('ilc_peps06',time_format = "num",stringAsFactors = TRUE)
ilc_lvps16 <-  get_eurostat('ilc_lvps16',time_format = "num",stringAsFactors = TRUE)
edat_lfs_9912 <-  get_eurostat('edat_lfs_9912',time_format = "num",stringAsFactors = TRUE)
lfsa_pfgacedm <-  get_eurostat('lfsa_pfgacedm',time_format = "num",stringAsFactors = TRUE)
lfst_r_lfur2gacu <-  get_eurostat('lfst_r_lfur2gacu',time_format = "num",stringAsFactors = TRUE)
lfst_r_eredcobu <-  get_eurostat('lfst_r_eredcobu',time_format = "num",stringAsFactors = TRUE)
```

<<<<<<< HEAD
=======
## Describe the data

`urb_cpopcb` is xxx, it has `r NROW(urb_cpopcb)` rows, `r NCOL(urb_cpopcb)` columns.

`ilc_di16` is xxx, it has `r NROW(ilc_di16)` rows, `r NCOL(ilc_di16)` columns.

`ilc_iw16` is xxx, it has `r NROW(ilc_iw16)` rows, `r NCOL(ilc_iw16)` columns.

`ilc_peps06` is xxx, it has `r NROW(ilc_peps06)` rows, `r NCOL(ilc_peps06)` columns.

`ilc_lvps16` is xxx, it has `r NROW(ilc_lvps16)` rows, `r NCOL(ilc_lvps16)` columns.

`edat_lfs_9912` is xxx, it has `r NROW(edat_lfs_9912)` rows, `r NCOL(edat_lfs_9912)` columns.

`lfsa_pfgacedm` is xxx, it has `r NROW(lfsa_pfgacedm)` rows, `r NCOL(lfsa_pfgacedm)` columns.

`lfst_r_lfur2gacu` is xxx, it has `r NROW(lfst_r_lfur2gacu)` rows, `r NCOL(lfst_r_lfur2gacu)` columns.

`lfst_r_eredcobu` is xxx, it has `r NROW(lfst_r_eredcobu)` rows, `r NCOL(lfst_r_eredcobu)` columns.

## Research Question

What decides the income level of 

## Introduce the variable

we introduce our variables in this part.



sex, age, country of birth, education level, income, (un)employment rate, 

## Clean the data

we clean our data set in this part.

`urb_cpopcb` is table of city-level population data by citizenship and country of birth, and we need to use `filter` method to extract our dataset.
for the indic_ur(urban audit indicator), we choose `DE2002I` (EU foreigners as a proportion of population), `DE2003I` (Non-EU foreigners as a proportion of population) and `DE2007I` Foreigners as a proportion of population`.

```{r}
urb_cpopcb|>filter(cities=='AT' & indic_ur=='DE2008I')
```
```{r}
urb_cpopcb|>filter(cities=='AT' & indic_ur=='DE2003I')
```

>>>>>>> e750cd88168600f6974a52b42b871f162b485d61


## Join the data

##


