---
title: "Data Processing"
author: "Jieyuan Yan, Puwen Wen"
format: html
---

## Prepare environment
```{r}
library(here)
library(vroom)
library(tidyr)
library(dplyr)
library(eurostat)
library(ggplot2)
```

## Read Dataset
```{r}
urb_cpopcb <- get_eurostat('urb_cpopcb',time_format = "num", stringsAsFactors = TRUE)
ilc_di16 <-  get_eurostat('ilc_di16',time_format = "num",stringAsFactors = TRUE)
ilc_iw16 <-  get_eurostat('ilc_iw16',time_format = "num",stringAsFactors = TRUE)
ilc_peps06 <-  get_eurostat('ilc_peps06',time_format = "num",stringAsFactors = TRUE)
ilc_lvps16 <-  get_eurostat('ilc_lvps16',time_format = "num",stringAsFactors = TRUE)
edat_lfs_9912 <-  get_eurostat('edat_lfs_9912',time_format = "num",stringAsFactors = TRUE)
lfsa_pfgacedm <-  get_eurostat('lfsa_pfgacedm',time_format = "num",stringAsFactors = TRUE)
lfst_r_eredcobu <-  get_eurostat('lfst_r_eredcobu',time_format = "num",stringAsFactors = TRUE)
edat_lfs_9915 <-  get_eurostat('edat_lfs_9915',time_format = "num",stringAsFactors = TRUE)
migr_imm8 <-  get_eurostat('migr_imm8',time_format = "num",stringAsFactors = TRUE)

demo_pjangroup <-  get_eurostat('demo_pjangroup',time_format = "num",stringAsFactors = TRUE)
```

`countries` is vector of all fields of EU contries.

`birth_eu` is vector of all fields of foreigners born in eu, given EU is changing overtime, we collect them together.

`birth_neu` is vector of all fields of foreigners born in non-eu, given EU is changing overtime, we collect them together.

```{r}
countries = c("BE","BG","CZ","DK","DE","EE","IE","EL","ES","FR","IT","CY","LV","LT","LU","HU","MT","NL","AT","PL","PT","RO","SI","SK","FI","SE","NO","CH","UK")
birth_eu = c("EU28_FOR","EU27_2007_FOR","EU27_2020_FOR")
birth_neu = c("NEU27_2007_FOR","NEU27_2020_FOR","NEU28_FOR")
```

<<<<<<< HEAD
=======
## Describe the original data file

### Overall summary

Raw data files before processing have different keys and measurement, so in overall summary we only present the column numbers and row numbers of each dataset. More detailed description for each data file is in the next subsection.

```{r}


# Organize data frames into a named list
data_list <- list(
  urb_cpopcb=urb_cpopcb,
  ilc_di16=ilc_di16,
  ilc_iw16=ilc_iw16,
  ilc_peps06=ilc_peps06,
  ilc_lvps16=ilc_lvps16,
  edat_lfs_9912=edat_lfs_9912,
  lfsa_pfgacedm=lfsa_pfgacedm,
  demo_pjangroup=demo_pjangroup,
  lfst_r_eredcobu=lfst_r_eredcobu,
  migr_imm8=migr_imm8
)

# Create the summary table
summary_table <- bind_rows(
  lapply(names(data_list), function(name) {
    data <- data_list[[name]]
    tibble(
      Data_Frame = name,
      Rows = nrow(data),
      Columns = ncol(data)
    )
  })
)

# View the summary table
print(summary_table)


```

### Detailed desccription for each data file

#### urb_cpopcb

```{r}

summary_urb_cpopcb <- urb_cpopcb |>
  filter((indic_ur%in% c('DE2003V','DE2002V'))&(cities%in%countries)) |> 
  ## we only use the country-level data
  group_by(indic_ur,cities) |>
  summarise(rows = n())
print(summary_urb_cpopcb)



```
#### ilc_di16
```{r}

ilc_di16 |> filter(unit=='PPS')

```





## Research Question

### Question 1
1. Does the scale of immigration influence the income of immigrants? To what extent does the immigration affect the economy of targeted countries?

With the first part of research, we can identify the concentration effect of immigrants on themselves. More precisely, whether the concentration of immigrants improve or decrease the welfare of immigrants.

In the first question, we take the immigrant scale (foreign-born population as a proportion in total population) as independent variable, and the median/average income(measured by purchasing power standard) of immigrants as dependent variable. To accurately identify the effect of immigration scale on immigrants' income, we keep the individual characteristics as constant(sex,age), and introduce some basic indicators of a country as controlled variables, including population, GDP, and inflation.

We also want to explore the immigration trend over time within a single country, which requires us to use time series data. Thus we collect the annual immigration data of each country, spanning between 2003 and 2023.

Simultaneity should be noticed so that we come to the second part of question. To what extent the immigration affect the economy of targeted countries? In this part we also conduct cross-national comparative analysis and time series for longitudinal impact. While this part has GDP as dependent variable and immigration scale as independent variable, and controlled variables keep the same.

Through this part of research, we can figure out the degree of significance of immigration for economic development of European countries.

The data panel used in two parts of this question is the same. 

To examine the validity of regression we implement Granger Causality Tests in the time series context, which test for the directional causality between immigration and economic changes.


### Question 2

2. What factors within immigrant group decide their employment rate? Compared to the native population, what are differences of these effects? What can we conclude from these differences on the mechanism of immigration impact on the economy of targeted countries?

In this question, we study the key determinants of employment rate of immigrant group, incorporating comprative analysis with natives and temporal dynamics of these determinants. For example, how do the effects of factors like education and urbanization on employment rates differ for immigrants versus the native population? Moreove, we can find from this question we can find how has the demographic structure of immigrants evolved during the last 20 years.

In this part, we take the employment rate as independent variable, using education/ages/sex/degree of urbanization/wage of the natives as regressors, and the immigration scale as a controlled variable. All these data are collected over time. 

Similar to the first question, we adopt Granger Causality Tests in the time series context, which test for the directional causality between immigration and economic changes.


## Introduce the variable

In this section we introduce some important variables.

### Panel A

`geo` indicates European country/region. Which country/region the abbreviations refer to can be consulted on Eurostat.

`c_birth` is a tag to distinguish foreigners born inside EU and those born outside EU, which allows us to seperately study the interior flexibility of EU citizens and the population influx from outside EU.

`Mean_income` of foreigners is measured by purchasing power standard, instead of Euros.

High education?

`immigration_ratio` is calculated by `Immigration_num` and `Pop_num`. 



## Clean the data

we clean our data set in this part.


```{r}
urb_cpopcb|>filter((indic_ur%in% c('DE2003V','DE2002V'))&(cities%in%countries)) |> 
            mutate(c_birth = ifelse(indic_ur == "DE2002V", "EU27_2007_FOR", 
                             ifelse(indic_ur == "DE2003V", "NEU27_2007_FOR", "Other")),
                   geo=cities)
```

<<<<<<< HEAD
>>>>>>> e750cd88168600f6974a52b42b871f162b485d61
=======
`ilc_di16` is table of median income, it contains different unit of measurement. Considering the inflation, we choose the PPS (Purchasing power standard)

```{r}
ilc_di16 |> filter(unit=='PPS')
```


# Basic Statistic Description 


# Plot the Data
```{r}
urb_cpopcb|>filter((indic_ur%in% c('DE2003V','DE2002V'))&(cities%in%countries))|>
  filter(cities=='DK')
# |>ggplot(aes(TIME_PERIOD,values))+geom_line()+facet_grid(vars(indic_ur))
```

```{r}
ilc_di16 |> filter((sex=='T')&(age=='Y_GE18')&(TIME_PERIOD==2003)&
    (indic_il=='MEI_E')&(unit=='PPS')&(geo=='AT'))

```


```{r}
migr_imm8|>filter((age=='TOTAL')&(sex=='T')&(agedef=='COMPLET')&(geo=='PL')) |>
  ggplot(aes(TIME_PERIOD,values))+geom_line()
```

```{r}
migr_imm8|>filter((age=='TOTAL')&(sex=='T')&(agedef=='COMPLET')&(geo%in%countries))
```


## Data Join

PanelA: first research question, consist of four 4 table

- tableA: mean income data, measured by Purchasing power standard, extracting all sex, all age, country of birth in EU or nonEU(considering the EU is changing overall, we use  `ifelse` to assign a fixed label), geo from EU countries.

- tableB: immigration number data, measured by number, extracting all sex, all age, complete age definition, geo from EU countries.

- tableC: education component data, measure by ratio(the ratio of the number of a specific education level immigrants to all imigrants). We extract all sex, all deg_urb, country of birth in EU or nonEU, geo from EU countries, and isced11 of ED5-8(Tertiary education). The main value is the ratio of Tertiary education immigrants to all immigrants in the same group.

- tableD: number of population, we extract geo and TIME_PERIOD level data.

Hence the Panel consists of several variables, geo, c_birth, TIME_PERIOD, Mean_income, Immigration_num, Highedu_ratio, Pop_num, and we compute a new variable `Imigration_ratio`, the ratio of Immigration to Total Population.

```{r}

A = ilc_di16 |> filter((sex=='T')&(age=='Y_GE18')&(c_birth%in%birth_neu | c_birth%in%birth_eu)&
    (indic_il=='MEI_E')&(unit=='PPS')&(geo%in%countries)) |> mutate(Mean_income=values) |>
    select(geo,c_birth,TIME_PERIOD,Mean_income)
A = A |> mutate( c_birth=ifelse(c_birth%in%birth_eu, "EU_FOR", 
             ifelse(c_birth%in%birth_neu, "NEU_FOR", "Other")))


B = migr_imm8|>filter((age=='TOTAL')&(sex=='T')&(agedef=='COMPLET')&(geo%in%countries)) |>
    mutate(Immigration_num=values) |> select(geo,TIME_PERIOD,Immigration_num)

C = edat_lfs_9915 |> filter((sex=="T")&(deg_urb=="TOTAL")&(geo%in%countries)&(isced11=="ED5-8")&
    (age=='Y15-64')&(c_birth%in%birth_neu | c_birth%in%birth_eu)) |> 
    mutate(Highedu_ratio=values)|>select(geo,c_birth,TIME_PERIOD,Highedu_ratio)
C = C |> mutate( c_birth=ifelse(c_birth%in%birth_eu, "EU_FOR", 
             ifelse(c_birth%in%birth_neu, "NEU_FOR", "Other")))

D = demo_pjangroup |> filter((sex=='T')&(age=='TOTAL')&(geo%in%countries))|>mutate(Pop_num=values)|>
  select(geo,TIME_PERIOD,Pop_num)


panelA = A |> inner_join(B, by = c("geo","TIME_PERIOD")) |> 
              inner_join(C, by = c("geo","TIME_PERIOD","c_birth")) |>
              inner_join(D, by = c("geo","TIME_PERIOD"))
panelA = panelA |> select(geo,c_birth,TIME_PERIOD,Mean_income,Immigration_num,Highedu_ratio,Pop_num) |>
          mutate(Imigration_ratio=Immigration_num/Pop_num)
panelA
```
```{r}
panelA |> ggplot(aes(Imigration_ratio,Mean_income))+geom_point()
```
```{r}
C
```


```{r}
edat_lfs_9915 |> filter((sex=="T")&(deg_urb=="TOTAL")&(geo%in%countries)&(isced11=="ED5-8")&
                          (age=='Y15-64')&(c_birth%in%birth_neu | c_birth%in%birth_eu)) |>
      arrange(TIME_PERIOD)
```
```{r}

lfst_r_eredcobu
```
```{r}

```
>>>>>>> 587a126bc7bb6fc86fe8905648a488b9cfb91ba4


## Join the data

##


