---
title: "Data Processing"
author: "Jieyuan Yan, Puwen Wen"
format: html
---
```{r}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

## Github Link

[click here](https://github.com/JacobinWen/QE-Dauphine-DM-Final-Project-Group-13)

## Prepare environment
```{r}
library(here)
library(vroom)
library(tidyr)
library(dplyr)
library(eurostat)
library(ggplot2)
```

## Read Dataset
```{r}
urb_cpopcb <- suppressMessages(get_eurostat('urb_cpopcb', time_format = "num", stringsAsFactors = TRUE))
ilc_di16 <- suppressMessages(get_eurostat('ilc_di16', time_format = "num", stringAsFactors = TRUE))
ilc_iw16 <- suppressMessages(get_eurostat('ilc_iw16', time_format = "num", stringAsFactors = TRUE))
ilc_peps06 <- suppressMessages(get_eurostat('ilc_peps06', time_format = "num", stringAsFactors = TRUE))
ilc_lvps16 <- suppressMessages(get_eurostat('ilc_lvps16', time_format = "num", stringAsFactors = TRUE))
edat_lfs_9912 <- suppressMessages(get_eurostat('edat_lfs_9912', time_format = "num", stringAsFactors = TRUE))
lfsa_pfgacedm <- suppressMessages(get_eurostat('lfsa_pfgacedm', time_format = "num", stringAsFactors = TRUE))
lfst_r_eredcobu <- suppressMessages(get_eurostat('lfst_r_eredcobu', time_format = "num", stringAsFactors = TRUE))
edat_lfs_9915 <- suppressMessages(get_eurostat('edat_lfs_9915', time_format = "num", stringAsFactors = TRUE))
migr_imm8 <- suppressMessages(get_eurostat('migr_imm8', time_format = "num", stringAsFactors = TRUE))
demo_pjangroup <- suppressMessages(get_eurostat('demo_pjangroup', time_format = "num", stringAsFactors = TRUE))
ilc_di03 <- suppressMessages(get_eurostat('ilc_di03', time_format = "num", stringAsFactors = TRUE))
```

`countries` is vector of all fields of EU countries.

`birth_eu` is vector of all fields of foreigners born in eu, given EU is changing overtime, we collect them together.

`birth_neu` is vector of all fields of foreigners born in non-eu, given EU is changing overtime, we collect them together. For example, we regard `EU28_FOR`, `EU27_2007_FOR`, and `EU27_2020_FOR` as foreigner born in Europe.

```{r}
countries = c("BE","BG","CZ","DK","DE","EE","IE","EL","ES","FR","IT","CY","LV","LT","LU","HU","MT","NL","AT","PL","PT","RO","SI","SK","FI","SE","NO","CH","UK")
birth_eu = c("EU28_FOR","EU27_2007_FOR","EU27_2020_FOR")
birth_neu = c("NEU27_2007_FOR","NEU27_2020_FOR","NEU28_FOR")
```



## Describe the data

Notice: All the fields used in data files could be found in `DataDescription.qmd`

### urb_cpopcb


Title: Population by citizenship and country of birth - cities and greater cities.

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/urb_cpopcb/default/table?lang=en&category=mi.mii.mii_urb)

Description: Contains population data classified by citizenship and country of birth for urban and metropolitan areas, enabling demographic and migration trend analyses.

Fields: freq, indic_ur, cities

Ranges: 1990-2024


### ilc_di16

Title: Mean and median income by group of country of birth (population aged 18 and over).

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/ilc_di16/default/table?lang=en&category=mi.mii.mii_soinc.mii_ip)

Description: Similar to ilc_di15 but focuses on grouping by country of birth, highlighting income disparities among native-born and foreign-born populations.

Fields: freq,unit,indic_il,c_birth,sex,age,geo

Ranges: 2003-2023


### ilc_lvps16

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/ilc_lvps16/default/table?lang=en&category=mi.mii.mii_soinc.mii_lc)

Title: Distribution of population by group of country of birth and tenure status (population aged 18 and over).

Description: Reports housing tenure types (e.g., owned or rented) across groups defined by country of birth.

Fields: freq,unit,tenure,c_birth,sex,age,geo

Ranges: 2003-2024


### edat_lfs_9912


Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/edat_lfs_9912/default/table?lang=en&category=mi.mii.mii_educ.mii_edata)

Title: Population by educational attainment level, sex, age, and country of birth (%).

Description: Shows educational attainment levels across demographic and migration status categories.

Fields: freq,unit,sex,isced11,c_birth,age,geo

Ranges: 2004-2023

### migr_imm8

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/migr_imm8$defaultview/default/table?lang=en)

Title: Immigration by age and sex

Fields: age,geo,sex,time,freq,unit

Ranges: 1990-2022

### demo_pjangroup

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/demo_pjangroup$defaultview/default/table?lang=en)

Title: Population on 1 January by age group and sex

Fields: age,geo,sex,time,freq,unit

Ranges: 1960-2023


### ilc_di03

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/ilc_di03$defaultview/default/table?lang=en)

Title: Mean and median income by age and sex

Fields: freq,unit,indic_il,c_birth,sex,age,geo

Ranges: 1995-2023


### demo_pjangroup

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/demo_pjangroup$defaultview/default/table?lang=en)

Title: Population on 1 January by age group and sex

Fields: age,geo,sex,time,freq,unit

Ranges: 1960-2023


### migr_imm8

Link: [Link to the data](https://ec.europa.eu/eurostat/databrowser/view/migr_imm8$defaultview/default/table?lang=en)

Title: Immigration by age and sex

Fields: age,geo,sex,time,freq,unit

Ranges: 1990-2022


## Summary

### Overall summary

Raw data files before processing have different keys and measurement, so in overall summary we only present the column numbers and row numbers of each dataset. More detailed description for each data file is in the next subsection.


```{r}


# Organize data frames into a named list
data_list <- list(
  urb_cpopcb=urb_cpopcb,
  ilc_di16=ilc_di16,
  ilc_iw16=ilc_iw16,
  ilc_peps06=ilc_peps06,
  ilc_lvps16=ilc_lvps16,
  edat_lfs_9912=edat_lfs_9912,
  lfsa_pfgacedm=lfsa_pfgacedm,
  demo_pjangroup=demo_pjangroup,
  lfst_r_eredcobu=lfst_r_eredcobu,
  migr_imm8=migr_imm8
)

# Create the summary table
summary_table <- bind_rows(
  lapply(names(data_list), function(name) {
    data <- data_list[[name]]
    tibble(
      Data_Frame = name,
      Rows = nrow(data),
      Columns = ncol(data)
    )
  })
)

print(summary_table)


```


## Basic Statistic Description for each data file with graphical representation

### urb_cpopcb

For simplicity, we only consider country-level data(instead of city-level data, which is scarce for each city), so we extract the country field in `cities`. For `indic_ur`(urban audit indicator), we extract rows of `DE2002V`(EU foreigners) and `DE2002V`(Non-EU foreigners), as these are two types of immigrants we desire to research. We extract our desired table and display some statistic characteristic as below.

```{r}
urb_cpopcb_filter = urb_cpopcb |>
  filter((indic_ur%in% c('DE2003V','DE2002V'))&(cities%in%countries))

summary_urb_cpopcb <-  urb_cpopcb_filter|> 
  summarise(rows = n(),.by = c("indic_ur","cities"))
```

After filtering, `urb_cpopcb` has `r NROW(urb_cpopcb_filter)` rows, and `r NCOL(urb_cpopcb_filter)` columns.

We display the number of valid data for each EU country. The distribution is not even, with some country having just 1 or 2 data sample, such as PL(Poland).
```{r}

summary_urb_cpopcb |> ggplot(aes(x=cities,y=rows,fill=indic_ur))+geom_bar(stat = "identity")+
  facet_wrap(vars(indic_ur),nrow = 2, ncol = 1) + theme(text = element_text(size = 10))

```
We display the immigrant trend for different countries. For simplicity, we choose some representative countries(based on the available sample), and show the number of immigrants across the sample years. The chosen countries are: BE(Belgium), FR(France), DE(Germany), SE(Sweden), NL(Netherlands), IT(Italy), FI(Finland), PT(Portugal), ES(Spain).

```{r}

urb_cpopcb_filter |> filter(cities%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |>
  ggplot(aes(TIME_PERIOD,values, color=indic_ur)) + geom_line() + 
  facet_wrap(~ cities, nrow = 3, ncol = 3, scales = "free")

```


### ilc_di16

This is a table of Mean and median income by group of country of birth.
Similarly, we extract our desired fields. For countries, (Note that now it's in `geo` column), we do it as above. For unit of measure, we adopt the `PPS`(Purchasing power standard), which is a more reasonable indicator compared with Euro (getting rid of money supply, inflation, etc.). For `indic_il`(income and living condition indicators), we choose `MEI_E`(Mean equivalised net income).

For the `c_birth`, as we illustrate before, the member of EU is changing, so we need to harmonise the calibre of statistics. We assign `EU_FOR` and `NEU_FOR` for both two categories.

```{r}
ilc_di16_filter = ilc_di16 |> 
  filter(unit=='PPS',geo%in%countries,indic_il=='MEI_E') |> 
  mutate( c_birth = case_when(
    c_birth %in% birth_eu ~ "EU_FOR",
    c_birth %in% birth_neu ~ "NEU_FOR",
    TRUE ~ c_birth ))

summary_ilc_dil6 <- ilc_di16_filter|>
  summarise(rows = n(),.by=c('geo','c_birth'))

```

After filtering, `ilc_di16` has `r NROW(ilc_di16_filter)` rows, and `r NCOL(ilc_di16_filter)` columns.

We display the figure as below. Similarly, we only show some of the countries.
After filtering, `ilc_di16_filter` has `r nrow(ilc_di16_filter)` rows, and `r ncol(ilc_di16_filter)` columns.

the figure is the average income group by countries, country of birth and sex


```{r}
ilc_di16_filter |> filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |>
  filter(age=='Y_GE18', c_birth%in%c("EU_FOR","NEU_FOR")) |>
  ggplot(aes(TIME_PERIOD,values, color=interaction(sex, c_birth))) + geom_line() + 
  facet_wrap(~ geo, nrow = 3, ncol = 3, scales = "free")
```
### ilc_di03

It's the table of Mean and median income by age and sex, which is used to compare the income level of immigrants with the overall level. We will use this table in the further analysis(regression).

We conduct the similar filter operation on the table.


```{r}
ilc_di03_filter = ilc_di03 |> filter(unit=='PPS',geo%in%countries,indic_il=='MEI_E')
```

After filtering, `ilc_di03` has `r NROW(ilc_di03_filter)` rows, and `r NCOL(ilc_di03_filter)` columns.


We display the trend of income level for different genders across country.
```{r}
ilc_di03_filter|>filter(age=="TOTAL") |>
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |>
  ggplot(aes(TIME_PERIOD,values, color=sex)) + geom_line() + 
  facet_wrap(~ geo, nrow = 3, ncol = 3, scales = "free")
```
We display the trend of income level for different age category across country.
```{r}
ilc_di03_filter|>filter(sex=="T")|>
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |>
  filter(age%in%c("Y16-24","Y25-49","Y50-64"))|>
  ggplot(aes(TIME_PERIOD,values, color=age)) + geom_line() + 
  facet_wrap(~ geo, nrow = 3, ncol = 3, scales = "free")
```

### ilc_iw16

It's the table of In-work at-risk-of-poverty rate by group of country of birth(population aged 18 and over). We conduct similar operation on this table (filter countries, assign new value to c_birth). 


```{r}
ilc_iw16_filter = ilc_iw16 |> 
  filter(geo%in%countries) |> 
  mutate( c_birth = case_when(
    c_birth %in% birth_eu ~ "EU_FOR",
    c_birth %in% birth_neu ~ "NEU_FOR",
    TRUE ~ c_birth ))

summary_ilc_iwl6 <- ilc_iw16_filter|>
  summarise(rows = n(),.by=c('geo','c_birth'))

```


After filtering, `ilc_iw16` has `r NROW(ilc_iw16_filter)` rows, and `r NCOL(ilc_iw16_filter)` columns.

We display the figures as below.
The figure is the at-risk-of-poverty rate grouped by country of birth, across different countries.

We display In-work at-risk-of-poverty rate as below.

```{r}
ilc_iw16_filter |> filter(age=='Y_GE18', sex=='T', c_birth!='NAT') |>  
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |>
  ggplot(aes(TIME_PERIOD,values, color=c_birth)) + geom_line() + 
  facet_wrap(~ geo, nrow = 3, ncol = 3, scales = "free")
```
The figure is the at-risk-of-poverty rate grouped by sex, across different countries.
```{r}
ilc_iw16_filter |> filter(age=='Y_GE18', c_birth=='FOR') |>  
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |>
  ggplot(aes(TIME_PERIOD,values, color=sex)) + geom_line() + 
  facet_wrap(~ geo, nrow = 3, ncol = 3, scales = "free")
```



### ilc_lvps16

Distribution of population by group of country of birth and tenure status.

We conduct similar operation on the table.

```{r}
ilc_lvps16_filter = ilc_lvps16 |> 
  filter(geo%in%countries) |> 
  mutate( c_birth = case_when(
    c_birth %in% birth_eu ~ "EU_FOR",
    c_birth %in% birth_neu ~ "NEU_FOR",
    TRUE ~ c_birth ))

summary_ilc_lvps16 <- ilc_lvps16_filter |> 
  filter(geo%in%countries)|>
  summarise(rows = n(),.by=c('geo','c_birth'))

```


The figure is the ratio of house own(rent) for immigrants by countries.

After filtering, `ilc_lvps16_filter` has `r nrow(ilc_lvps16_filter)` rows, and `r ncol(ilc_lvps16_filter)` columns.

```{r}

ilc_lvps16_filter |> filter(age=="Y_GE18",sex=="T",c_birth%in%c('FOR')) |>
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |> 
  ggplot(aes(TIME_PERIOD,values,color=tenure))+
  geom_bar(stat = 'identity')+facet_wrap(~geo, nrow = 3, ncol = 3, scales = "free")


```
### edat_lfs_9912

It's table of Population by educational attainment level, sex, age, and country of birth (%).
```{r}
edat_lfs_9912_filter = edat_lfs_9912 |> filter(geo%in%countries) |> 
  mutate( c_birth = case_when(
    c_birth %in% birth_eu ~ "EU_FOR",
    c_birth %in% birth_neu ~ "NEU_FOR",
    TRUE ~ c_birth ))

summary_edat_lfs_9912 <- edat_lfs_9912_filter |> 
  filter(geo%in%countries)|>
  group_by(geo,c_birth) |>
  summarise(rows = n())
```

After filtering, `urb_cpopcb` has `r NROW(edat_lfs_9912_filter)` rows, and `r NCOL(edat_lfs_9912_filter)` columns.


For simplicity, we display the education attainment level for immigrants (EU foreigner and NEU foreigner) of France.
```{r}

edat_lfs_9912_filter |> filter(geo=='FR',age=='Y18-64',sex=='T') |>
  filter(isced11%in%c('ED0-2','ED3_4','ED5-8'),c_birth%in%c('EU_FOR','NEU_FOR')) |>
  ggplot(aes(TIME_PERIOD,values,color=isced11))+geom_bar(stat='identity')+
  facet_wrap(~ c_birth)

```


### demo_pjangroup

It is the table of Population.
We extract EU countries, and display the population trend by sex and countries as below.
```{r}
demo_pjangroup_filter = demo_pjangroup |> filter(geo%in%countries,sex!="T", age=="TOTAL")
summary_demo_pjangroup <- demo_pjangroup_filter |> 
  summarise(rows = n(),.by=geo)

```

`demo_pjangroup` has `r NROW(demo_pjangroup_filter)` rows and `r NCOL(demo_pjangroup_filter)` columns.

```{r}
demo_pjangroup_filter |> 
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |> 
  ggplot(aes(TIME_PERIOD,values,color=sex))+
  geom_line()+facet_wrap(~geo,scales = "free")
```

### migr_imm8

It is the table of Population of immigrants.

We display the trend of immigrants by sex as below.
```{r}
migr_imm8_filter = migr_imm8|> filter(geo%in%countries,agedef=="COMPLET",age=="TOTAL")
summary_migr_imm8 <- migr_imm8_filter |> 
  summarise(rows = n(),.by=geo)

```

`migr_imm8` has `r NROW(migr_imm8_filter)` rows and `r NCOL(migr_imm8_filter)` columns.

```{r}
migr_imm8_filter|> filter(sex!="T")|>
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |> 
  ggplot(aes(TIME_PERIOD,values,color=sex))+geom_line()+facet_wrap(~geo,scales="free")
```


```{r}
migr_imm8_filter|> filter(sex!="T")|>
  filter(geo%in%c("BE","FR","DE","SE","NL","IT","FI","PT","ES")) |> 
  ggplot(aes(TIME_PERIOD,values,color=sex))+geom_line()+facet_wrap(~geo,scales="free")
```


## Research Question

### Question 1

Does the scale of immigration influence the income of immigrants? To what extent does the immigration affect the economy of targeted countries?

With the first part of research, we can identify the concentration effect of immigrants on themselves. More precisely, whether the concentration of immigrants improve or decrease the welfare of immigrants.

In the first question, we take the immigrant scale (foreign-born population as a proportion in total population) as independent variable, and the median/average income(measured by purchasing power standard) of immigrants as dependent variable. To accurately identify the effect of immigration scale on immigrants' income, we keep the individual characteristics as constant(sex,age), and introduce some basic indicators of a country as controlled variables, including population, GDP, and inflation.

We also want to explore the immigration trend over time within a single country, which requires us to use time series data. Thus we collect the annual immigration data of each country, spanning between 2003 and 2023.

Simultaneity should be noticed so that we come to the second part of question. To what extent the immigration affect the economy of targeted countries? In this part we also conduct cross-national comparative analysis and time series for longitudinal impact. While this part has GDP as dependent variable and immigration scale as independent variable, and controlled variables keep the same.

Through this part of research, we can figure out the degree of significance of immigration for economic development of European countries.

The data panel used in two parts of this question is the same. 

To examine the validity of regression we implement Granger Causality Tests in the time series context, which test for the directional causality between immigration and economic changes.


### Question 2

What factors within immigrant group decide their income? Compared to the native population, what are differences of these effects? What can we conclude from these differences on the mechanism of immigration impact on the economy of targeted countries?

In this question, we study the key determinants of income of immigrant group, incorporating comparative analysis with natives and temporal dynamics of these determinants. For example, how do the effects of factors like education and urbanization on income level differ for immigrants versus the native population? Are there any difference for immigrants from EU countries and non-EU countries? Moreover, we can find from this question how has the demographic structure of immigrants evolved during the last 20 years.

In this part, we take the employment rate as independent variable, using education/sex/domestic wage as regressors, and the immigration scale as a controlled variable. All these data are collected over time. 

Similar to the first question, we adopt Granger Causality Tests in the time series context, which test for the directional causality between immigration and economic changes.


## Data Cleaning and Joining

Corresponding to two research questions, we design two data panels. In this part we clean and join the raw data file.

### PanelA

PanelA: first research question, consist of four 4 table

- tableA: mean income data, measured by Purchasing power standard, extracting all sex, all age, country of birth in EU or nonEU(considering the EU is changing overall, we use  `ifelse` to assign a fixed label), geo from EU countries.

- tableB: immigration number data, measured by number, extracting all sex, all age, complete age definition, geo from EU countries.

- tableC: education component data, measure by ratio(the ratio of the number of a specific education level immigrants to all immigrants). We extract all sex, country of birth in EU or nonEU, geo from EU countries, and isced11 of ED5-8(Tertiary education). The main value is the ratio of Tertiary education immigrants to all immigrants in the same group.

- tableD: number of population, we extract geo and TIME_PERIOD level data.

- tableE: mean income data for domestic, we extract geo and TIME_PERIOD level data.

Hence the Panel consists of several variables, geo, c_birth, TIME_PERIOD, Mean_income, Immigration_num, Highedu_ratio, Pop_num, and we compute a new variable `Imigration_ratio`, the ratio of Immigration to Total Population.


```{r}

A = ilc_di16 |> filter((sex=='T')&(age=='Y_GE18')&(c_birth%in%birth_neu | c_birth%in%birth_eu)&
    (indic_il=='MEI_E')&(unit=='PPS')&(geo%in%countries)) |> mutate(Mean_income_FOR=values) |>
    select(geo,c_birth,TIME_PERIOD,Mean_income_FOR)
A = A |> mutate( c_birth=ifelse(c_birth%in%birth_eu, "EU_FOR", 
             ifelse(c_birth%in%birth_neu, "NEU_FOR", "Other")))


B = migr_imm8|>filter((age=='TOTAL')&(sex=='T')&(agedef=='COMPLET')&(geo%in%countries)) |>
    mutate(Immigration_num=values) |> select(geo,TIME_PERIOD,Immigration_num)

C = edat_lfs_9912 |> filter((sex=="T")&(geo%in%countries)&(isced11=="ED5-8")&
    (age=='Y15-64')&(c_birth%in%birth_neu | c_birth%in%birth_eu)) |> 
    mutate(Highedu_ratio=values)|>select(geo,c_birth,TIME_PERIOD,Highedu_ratio)
C = C |> mutate( c_birth=ifelse(c_birth%in%birth_eu, "EU_FOR", 
             ifelse(c_birth%in%birth_neu, "NEU_FOR", "Other")))

D = demo_pjangroup |> filter((sex=='T')&(age=='TOTAL')&(geo%in%countries))|>mutate(Pop_num=values)|>
  select(geo,TIME_PERIOD,Pop_num)

E = ilc_di03|> filter((sex=="T")&(age=="Y_GE18")&(geo%in%countries)&(unit=="PPS")&(indic_il=="MEI_E"))|>
  mutate(Mean_income_NAT = values)|>select(geo,TIME_PERIOD,Mean_income_NAT)


panelA = A |> inner_join(B, by = c("geo","TIME_PERIOD")) |> 
              inner_join(C, by = c("geo","TIME_PERIOD","c_birth")) |>
              inner_join(D, by = c("geo","TIME_PERIOD")) |>
              inner_join(E, by = c("geo","TIME_PERIOD"))
panelA = panelA |> select(geo,c_birth,TIME_PERIOD,Mean_income_FOR,Mean_income_NAT,Immigration_num,Highedu_ratio,Pop_num) |>
          mutate(Imigration_ratio=Immigration_num/Pop_num)
panelA
```


PanelA has `r NROW(panelA)` rows and `r NCOL(panelA)`.

We plot the scatter chart of `Imigration_ratio` and `Mean_income_FOR`as below.

We can see a roughly postive relation between `Imigration_ratio` and `Mean_income_FOR`, across all EU contries, no matter born in EU or nonEU.

Note that it's just a basic display, which cannot lead to final conclusion. Strictly, we should control the income level of domestic.

PanelA has `r nrow(panelA)` rows and `r ncol(panelA)`.

```{r}
panelA |> ggplot(aes(Imigration_ratio,Mean_income_FOR,color=geo))+geom_point()
```


```{r}
panelA |> ggplot(aes(Imigration_ratio,Mean_income_FOR,color=geo))+geom_point()+
  facet_wrap(~c_birth)
```


### PanelB

we only consider people aged between 18 and 64, which is regarded as labor age.

PanelB: the second research question, consist of four 5 table

- tableF: mean income data for immigrants, measured by Purchasing power standard, extracting sex(Male and Female), age between 18 and 64, country of birth in EU or nonEU(considering the EU is changing overall, we use  `ifelse` to assign a fixed label), geo from EU countries.

- tableG: education component data, measure by ratio(the ratio of the number of a specific education level immigrants to all imigrants). We extract sex of male and female, country of birth in EU or nonEU, geo from EU countries, and isced11 of ED0-2, ED3-4, and ED5-8(Tertiary education). We use `pivot_wider` to transfer isced11 into columns.

- tableH: mean income data for domestic, measured by Purchasing power standard, extracting sex(Male and Female), age between 18 and 64.

- tableI: number of immigrants, we extract sex of males and female, age between 18 and 64, geo of EU countries and TIME_PERIOD level data, and we aggregate the sum of immigrants grouped by sex, geo, and TIME_PERIOD.

- tableJ: number of population, we extract sex of total, age between 15 and 64(because there is no field starting from 18, we use 15 as complement), geo of EU countries and TIME_PERIOD level data, and we aggregate the sum of immigrants grouped by geo, and TIME_PERIOD.

Hence the Panel consists of several variables, `geo`, `c_birth`, `TIME_PERIOD`, `Income_FOR`, `Immigration_num`, `ED0-2`, `ED3_4`, `ED5-8`, `Pop_num`, `Income_Dom`, and we compute a new variable `Imigration_ratio`, the ratio of Immigration to Total Population.

```{r}
F = ilc_di16 |> filter(geo%in%countries,unit=='PPS',age=='Y18-64',
                       indic_il=='MEI_E',sex!='T')|>
    mutate(c_birth=case_when(c_birth %in% birth_eu ~ "EU_FOR",
      c_birth %in% birth_neu ~ "NEU_FOR",TRUE ~ c_birth ))|>
    filter(c_birth%in%c('EU_FOR','NEU_FOR')) |>
    mutate(Income_FOR=values) |>
    select(sex,geo,c_birth,TIME_PERIOD,Income_FOR)

G = edat_lfs_9912|>filter(age=="Y18-64",geo%in%countries,) |>
    filter(isced11%in%c("ED0-2","ED3_4","ED5-8")) |>
    mutate(c_birth=case_when(c_birth %in% birth_eu ~ "EU_FOR",
      c_birth %in% birth_neu ~ "NEU_FOR",TRUE ~ c_birth ))|>
    filter(c_birth%in%c('EU_FOR','NEU_FOR')) |> 
    pivot_wider(names_from = isced11, values_from = values) |>
    select(sex,c_birth,geo,TIME_PERIOD,`ED0-2`,`ED3_4`,`ED5-8`)

H = ilc_di03 |> filter(geo%in%countries,unit=='PPS',age=='Y18-64',
        indic_il=='MEI_E',sex!='T') |>
    mutate(Income_Dom=values) |>
    select(sex,geo,TIME_PERIOD,Income_Dom)

I = migr_imm8 |> filter(sex!="T",agedef=='COMPLET') |> 
  filter(age%in%paste0("Y", 18:64),geo%in%countries) |>
  summarise(Immigration_num=sum(values),.by=c("geo","sex","TIME_PERIOD"))

J = demo_pjangroup |> filter(sex=='T',geo%in%countries,) |>
  filter(age%in%c("Y15-19","Y20-24","Y25-29","Y30-34","Y35-39",
                  "Y40-44","Y45-49","Y50-54","Y55-59","Y60-64")) |>
  summarise(Pop_num=sum(values),.by=c("geo","TIME_PERIOD"))

panelB = F |> inner_join(G, by = c("sex","c_birth","geo","TIME_PERIOD")) |>
              inner_join(H, by = c("sex","geo","TIME_PERIOD")) |>
              inner_join(I, by = c("geo","sex","TIME_PERIOD")) |>
              inner_join(J, by = c("geo","TIME_PERIOD"))|> 
        mutate(Imigration_ratio=Immigration_num/Pop_num)
panelB
```

After a series of operation, we get other panel for the second question. 

`panelB` has `r NROW(panelB)` rows and `r NCOL(panelB)` columns.

## Introduce the variable

In this section we introduce some important variables, and explain our process of constructing our regression panel. Our operation include data joining, aggregating, and so on.

### Panel A

Panel A is designed for the first research question, consist of four 4 table

`geo` indicates European country/region. Which country/region the abbreviations refer to can be consulted on Eurostat.

`c_birth` is a tag to distinguish foreigners born inside EU and those born outside EU, which allows us to separatly study the interior flexibility of EU citizens and the population influx from outside EU.

`Mean_income` of foreigners is measured by purchasing power standard, instead of Euros.

`High education`: the ratio of immigrants attaining high education to the overall number.

`immigration_ratio` is calculated by `Immigration_num` and `Pop_num`. 

### Panel B

Panel B is designed for the second research question, consist of 5 tables.

Similar to panel A, `geo` indicates European country/region. `c_birth` is also similar.

Column `Income_FOR` is the variable of foreigners' income, `Income_Dom` is natives' income. We introduce the latter to control the effect of targeted countries economic prosperity.

In this panel we adopt more detailed divisions by education level.

`ED0-2`, `ED3-4`,`ED5-8` are indicators of education level, `ED0-2` represents relatively low education level,(e.g.elementary school), `ED3-4` represents intermediate level(e.g. High school degree),`ED5-8` represents relatively high education level(university degree or equivalent).

`Income_Dom` is the newly introduced control variable, our study can filter partly eliminate the simultaneity problem in regression.

`immigration_ratio` is calculated by `Immigration_num` and `Pop_num`. 


## Further Analysis

When this document comes to an end, we should point out the possibility of extension of this study. In the two research questions, there are other potential variables that can be taken into account.

### Additional Variables

For example the tenant status of immigrants. But the effect of these variables are not obvious, we will try to incorporate these variables during the study, but might possibly find their correlation with other variables or irrelevance. Thus for the final result of this study, the mechanism or regression model can be modified.

### Regional Analysis

We notice that the data of the degree of urbanization is available on Eurostat, this could help us to uncover heterogeneities that a national-level analysis might obscure. Comparing metropolitan versus rural areas within countries to assess if urbanization intensifies or mitigates the effects of immigration on income.

#### Regression For Question2

To account for differences in income levels across countries, we adopt a relative measurement defined as the ratio of immigrant income `Income_FOR` to native income `Income_Dom`, referred to as `Income_Rev`.

For the educational aspect, since the sum of `ED0-2`, `ED3_4` and `ED5-8` always equals 1, we exclude one category to avoid multicollinearity and use the remaining two as independent variables.

For the sex variable, we create a dummy variable, denoted as `sex_onehot`, where 1 indicates male and 0 indicates female.

Similarly, for the `c_birth` variable, we define a dummy variable, where 1 represents EU-born immigrants (EU_FOR) and 0 represents non-EU-born immigrants

To ensure consistent data scaling, the `immigration_ratio` is multiplied by 100 and redefined as `Imm_ratio`.

Finally, to account for potential time effects or trends, we include lagged variables for both `Income_Rev` and `Imm_ratio`.

Overall, we exclude rows with null values from the dataset.
```{r}
panelB |> mutate(Income_Rev=Income_FOR/Income_Dom) |>
  mutate(Income_Rev_lag1=lag(Income_Rev,1),.by=c("geo","sex","c_birth"))
```


```{r}
# panelB 
panelB_reg = panelB |> mutate(Income_Rev=(Income_FOR/Income_Dom),
                              Imm_ratio=Imigration_ratio*100) |> 
  mutate(Income_Rev_lag1=lag(Income_Rev, 1), 
         Imm_ratio_lag1=lag(Imm_ratio,1),.by=c("geo","sex","c_birth")) |>
  mutate(Income_Rev_lag2=lag(Income_Rev, 2), 
         Imm_ratio_lag2=lag(Imm_ratio,2),.by=c("geo","sex","c_birth")) |>
  filter(!is.na(Income_Rev_lag2),!is.na(Income_Rev_lag1),!is.na(Income_Rev),
         !is.na(Imm_ratio),!is.na(Imm_ratio_lag1),!is.na(Imm_ratio_lag2),
         !is.na(`ED5-8`),!is.na(ED3_4)) |>
  mutate(`ED0-2`=100-`ED5-8`-ED3_4) |>
  mutate(`ED0-2`=`ED0-2`/100,`ED5-8`=`ED5-8`/100)|>
  mutate(sex_onehot=case_when(sex=='F'~0,sex=='M'~1)) |>
  mutate(c_birth_onehot=case_when(c_birth=='NEU_FOR'~0,c_birth=='EU_FOR'~1)) |>
  mutate(sex_birth_onehot=sex_onehot*c_birth_onehot) |>
  select(Income_Rev,Income_Rev_lag1,Income_Rev_lag2,sex_onehot,c_birth_onehot,
         sex_birth_onehot,`ED0-2`,`ED5-8`,Imm_ratio,Imm_ratio_lag1,Imm_ratio_lag2)
```

We have a look at our regression panel.
`panelB_reg` has `r NROW(panelB_reg)` rows and `r NCOL(panelB_reg)` columns.

We display the distribution of Income_Rev. We can see that `Income_Rev` vary from 0.5 to 2. In some groups, the relative level of income is only half compared to native income, while some reaching 1.8.
```{r}
panelB_reg |> ggplot(aes(Income_Rev))+geom_density()
```
We propose some hypothesis before we run the regression.

- Hypothesis 1: The relative income level is not influenced by gender.

- Hypothesis 2: The relative income level does not vary based on the country of birth of immigrants (EU vs. Non-EU).

- Hypothesis 3: The relative income level is not affected by education.

- Hypothesis 4: The relative income level is not influenced by clustering effects (e.g., higher immigration leading to increased competition and lower income).

We run our regression as below and display the basic summary result.
```{r}
modelB <- lm(Income_Rev~Income_Rev_lag1+Income_Rev_lag2+
               sex_onehot+c_birth_onehot+sex_birth_onehot+
               `ED0-2`+`ED5-8`+Imm_ratio+Imm_ratio_lag1+Imm_ratio_lag2,panelB_reg)
summary(modelB)
```
From the regression table, we observe the following:
1. The relative income level exhibits strong autocorrelation.
2. Gender does not have a significant effect on the relative income level; therefore, we cannot reject Hypothesis 1.
3. The country of birth is significantly and positively correlated with the relative income level, indicating that immigrants born in EU countries have higher relative incomes than those from non-EU countries. Hence, we reject Hypothesis 2.
4. A higher fraction of immigrants within a group receiving low education is strongly negatively correlated with the relative income level. This demonstrates that education significantly impacts income, leading us to reject Hypothesis 3.
5. The immigration ratio has a significantly negative effect on relative income, meaning we can reject Hypothesis 4.

Based on this result, we have some suggestions.

- Since gender does not significantly affect relative income levels, this suggests that EU countries have made substantial progress in addressing gender inequality.

- The positive correlation between EU-born immigrants and higher relative income levels indicates a potential disparity in economic opportunities between immigrants from EU and non-EU countries. Policies should focus on improving integration and access to opportunities for non-EU immigrants by offering tailored language training, skill development programs, and mentoring initiatives.

- The significant negative correlation between low education levels and relative income indicates that individuals with low education earn well below the native average and are more likely to experience poverty. Policymakers should pay more attention to this group by providing greater access to educational opportunities. 

- The insignificant but slightly negative effect of immigration ratios suggests that when immigrants are concentrated in one country, competition among them increases, potentially lowering their income. This implies that policymakers should carefully regulate the influx of immigrants, particularly illegal ones.


### Policy impact

In modern states immigration is a subject highly influenced by related policy. European Union has adopted several policies on immigration problem, which somehow cause larger scale of refugee influx. We can particularly find the data just before or after the implementation of those policies and conduct Difference-in-Difference analysis to assess the impact of policy.


By exploring these new dimensions, our study could evolve into a broader framework that not only addresses current research questions but also contributes to understanding of immigration's multifaceted impacts.





